fGFPCA dynamic prediction

### 2023-01-25 f-GFPCA.Rmd
try laplace demon package

>>>>

#### Explicit laplace approximation

- Idea: the posterior distribution approaches a Gaussian distribution as sample size grows. 
- <span style="color: red;"> Looks like it is also maximizing posterior log-likelihood </span>
- <span style="color: red;"> How to use Laplace Approximation to approximate integrals? </span>

https://search.r-project.org/CRAN/refmans/LaplacesDemon/html/LaplaceApproximation.html
